|

### 2021-06-02 03-Chp-Systematic-Review.Rmd
End of day: -3432

## To Do

-   Examine how many times a primary study was included in a review\
-   Look at whether searching preprints made any difference to my results
-   Could apply ROBIS to previous reviews to see how they stack-up? (This may be done as part of Georgia's summer project)

## Extra studies to include:

* Smeet et al. reference in the CPRD analysis
* Larsson - 10.1136/bmj.j5375 [@larsson2017b]
* Statins and the risk of dementia Jick

@@

## Additional ideas

-   Evidence map - show the distribution of the different studies population across the world.
-   Living systematic review approach - update weekly based on medRxiv

## Aims

@@

Based on the review of prev, no previous evidence synthesis exercise attempted to examine all available literature simultaneously.

Only by looking across all available evidence can

@@

@@

The full search strategy for the Medline search, which was designed first and subsequently translated into the syntax for other databases is presented in Appendix \@ref(appendix-search-strategy).

@@

@@

This analysis was unusual, as multiple methods of intergration and analysis were required with data spannign many forms.

@@

@@

@@

<!-- TODO This next bit is not true -->

@@

## Studification

@@

## Following up with authors

@@

A summary of this tool is contained in Appendix \@ref (), .

@@

```{r prisma-flow-setup, results="hide", message=FALSE}
```

@@

(ref:prisma-flow-scap) PRISMA Flowchart

@@

Following de-duplication, the titles and abstracts of 16109 records were assessed for eligibility. 387 were deemed potentially eligible and the full text records for these were requested and screened. \@ref(fig:prisma-flow-fig)

@@

@@

-   PRISMA Flowchart (use PRISMA2020 from GitHub - depending on level of involvement, could refer to the Appendix here too.)

@@

@@

@@

<!-- Will to get actual numbers for this section -->

@@

@@

<!-- Triple check whether any of the studies have yet to be published -->

@@

### Searching for/including Mendelian randomisation studies

@@

Potentially missing other Mendelian randomisation studies, as we identified some through our snowball searching that were not captured by the search strategy. An example is Larsson et al. 2017[@larsson2017a], where the study examined the association between lipid fractions

Comment on the fact that several of the studies identified through the search of preprints, were subsequently published, but much later than the

@@

Test

>>>>

<!-- ## To Do -->

<!-- -   TODO Examine how many times a primary study was included in a review\ -->
<!-- -   TODO Look at whether searching preprints made any difference to my results -->
<!-- -  TODO Could apply ROBIS to previous reviews to see how they stack-up? (This may be done as part of Georgia's summer project) -->

<!-- TODO Extra studies to include: -->

<!-- * Smeet et al. reference in the CPRD analysis -->
<!-- * Larsson - 10.1136/bmj.j5375 [@larsson2017b] -->
<!-- * Statins and the risk of dementia Jick -->

@@

As introduced in previous chapters,

<!-- IDEA Evidence map - show the distribution of the different studies population across the world. Distribution will have to be of participants, not primary authors. Though could use to show how data is being used globally -->

## Introduction {#sys-rev-intro}

@@

Based on the review of existing literature, no previous evidence synthesis exercise attempted to examine all available literature simultaneously.

Only by looking across all available evidence can the true, given the often limited use of one type of evidence (RCTs are hard to do, obs studies are biased).

@@

<!-- TODO Look at citation chaser for this, but have a cut-off publication date of  -->

@@

The full search strategy for the Medline search, which was designed first and subsequently translated into the syntax for other databases is presented in Appendix \@ref(appendix-search-strategy). A summary by topic is presented in Table

<!----------------------------------------------------------------------------->
(ref:searchOverview-caption) Summary of systematic search by topic. For a full list of search terms, see Appendix \@ref()

(ref:searchOverview-scaption) searchOverview

```{r searchOverview-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

@@

<!-- TODO Expand on rationale for exclusion of cross-sectional studies. Dementia is a disease severly at risk of differential recall, leading to misclassification bias. By using prospective studies, the potential for this bias is reduced. -->

@@

This analysis was unusual, as multiple methods of integration and analysis were required with data spanning many forms.

A piloted data extraction for was used. I extracted the data in the first instance and subset was checked by a colleague for accuracy.

@@

#### Randomised controlled trials

@@

#### Non-randomised studies of interventions

@@

#### Mendelian randomisation studies

<!-- TODO This next bit is not all true -->

@@

### Studification

@@

### Following up with authors

@@

This tool grew out of a collaboration with other reserachers to design a modular method for creating these plots <!-- Apparently collaboration is a big thing they want to see -->

A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this analysis were created using

.

@@

```{r prisma-flow-setup, include = FALSE}
```

@@

(ref:prisma-flow-scap) PRISMA Flow Diagram

@@

Following de-duplication, the titles and abstracts of `r hold()` records were assessed for eligibility. `r hold()` were deemed potentially eligible and the full text records for these were requested and screened. \@ref(fig:prisma-flow-fig)

@@

As shown in

@@

-   PRISMA Flowchart

@@

Many studies did not report the codelists used to run the analysis,

@@

<!-- TODO Have a look at this -->

@@

<!-- TODO Will have to get actual numbers for this section -->

@@

Good example is [https://doi.org/10.1101/168674](https://doi.org/10.1101/168674), which was subsequently published in Nature Comms but in 2020, following peer-review (found no impact of LDL-c on AD following removal of APOE4).

@@

<!-- TODO Triple check whether any of the studies have yet to be published. Chose a given date and go from there -->

@@

@@

#### Inclusion of Mendelian randomisation studies

Potentially missing other Mendelian randomisation studies, as we identified some through our snowball searching that were not captured by the search strategy. An example is Larsson et al. 2017[@larsson2017a], where the study examined the association between lipid fractions with Azlheimer's disease.

Potentially the use of methods such as snowballing (forwards and backwards citation chasing) should attenuate the bias introduced by this method.

However, in future reviews, a dedicated search for "risk factors" and "dementia" and "

#### Inclusion of preprints

Comment on the fact that several of the studies identified through the search of preprints, were subsequently published, but much later than the
cut-off point for the search (e.g. they would not have been captured by the search fot published papers)

@@

### Use in other chapters

Findings from this review are used though out the subsequent chapters.

For example,

### 2021-06-02 front-and-back-matter/99-appendices.Rmd
End of day: -3432

# By Chapter {#chapter-appendix-heading}

## Chapter \@ref(intro-heading) {#appendix-into}

### Publications beyond the scope of this thesis {#appendix-publications}

@@

## Chapter \@ref(sys-rev-tools-heading) {#appendix-sys-rev-tools}

@@

### Code to search preprints {#appendix-medrxivr-code}

@@

topic1 <- c("statin",
            mx_caps("ldl"),
            mx_caps("hdl"),
            mx_caps("TG"),
            paste0("\\b",mx_caps("TC"),"\\b"),
            "ezetim",
            "lipoprotein",
            "lipid",
            "cholesterol")

@@

test <- mx_search(bx_data, query)

test2 <- mx_search(mx_data, query)

@@

### MR risk of bias tool {#appendix-mr-rob}

## Chapter \@ref(sys-rev-heading) {#appendix-sys-rev}

## Chapter \@ref(cprd-analysis-heading) {#appendix-cprd-analysis}

### Amendments to protocol {#appendix-cprd-amendments}

### Code lists

## Chapter \@ref(discussion-heading)

### Catalogue of failures

@@

# Other Appendix {#other-appendix-heading}

@@

## Producing risk-of-bias visualisations with `robvis` {#appendix-robvis}

@@

>>>>

<!----------------------------------------------------------------------------->
# By Chapter {#chapter-appendix-heading}

<!----------------------------------------------------------------------------->
## Chapter \@ref(intro-heading) {#appendix-into}

<!----------------------------------------------------------------------------->
### Publications beyond the scope of this thesis {#appendix-publications}

@@

## Chapter \@ref(sys-rev-tools-heading) {#appendix-sys-tools}
<!----------------------------------------------------------------------------->

@@

<!----------------------------------------------------------------------------->
### Code to search preprints {#appendix-medrxivr-code}

@@

topic1 <- c(mx_caps("statin"),
            mx_caps("ldl"),
            mx_caps("hdl"),
            mx_caps("TG"),
            mx_caps("triglycer"),
            paste0("\\b",mx_caps("TC"),"\\b"),
            mx_caps("ezetim"),
            mx_caps("fibrate"),
            mx_caps("bile acid"),
            mx_caps("lipoprotein"),
            mx_caps("lipid"),
            mx_caps("cholesterol"))

@@

bx_results <- mx_search(bx_data, query)

mx_results <- mx_search(mx_data, query)

@@

<!----------------------------------------------------------------------------->
### MR risk of bias tool {#appendix-mr-rob}

<!----------------------------------------------------------------------------->
## Chapter \@ref(cprd-analysis-heading) {#appendix-cprd-analysis}
<!----------------------------------------------------------------------------->
### Amendments to protocol {#appendix-cprd-amendments}

<!----------------------------------------------------------------------------->
### Code lists

## Chapter \@ref(ipd-heading) {#appendix-ipd-analysis}
<!----------------------------------------------------------------------------->
### Section 1

<!----------------------------------------------------------------------------->
### Section 2

<!----------------------------------------------------------------------------->
## Chapter \@ref(discussion-heading)

<!----------------------------------------------------------------------------->
### Catalogue of failures

@@

<!----------------------------------------------------------------------------->
# Other Appendix {#other-appendix-heading}

@@

<!----------------------------------------------------------------------------->
## Producing risk-of-bias visualisations with `robvis` {#appendix-robvis}

@@

## Creating

### 2021-06-02 front-and-back-matter/_acknowledgements.Rmd
End of day: -3432

@@

Thanks to the creator of the oxfordown which was used

@@

robvis contributors

Annual reviewersLn Rupert Payne and Emma Anderson

<!-- I am a Wellcome Trust Funded PhD student with grant code 102432/Z/13/Z. The funding source had no role in the design, conduct of the study, collection, management, analysis and interpretation or preparation, review, or approval of the thesis. -->

Statistical support:

All authors who volunteered time and effort

>>>>

<!-- TODO CHECK ALL NAME SPELLINGS -->

@@

@@

robvis contributors: (there are at least 3)

Annual reviewers: Rupert Payne and Emma Anderson

Those who contributed their time to dual marking papers and code with me,

I am a NIHR Doctoral Research Fellow with grant code **TBC**. The funding source had no role in the design, conduct of the study, collection, management, analysis and interpretation or preparation, review, or approval of the thesis.

Statistical support: check emails!

All authors who volunteered time and effort to provided

A special thanks goes out to Mark Newbury of the

Finally, thanks to parents and Ciara Gardiner.
